Persistence of seed mixture species: <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-18 R/model_fcs_markdown.Rmd
Update

```{r}
sites %>% group_by(exposition) %>% count(site)
boxplot(sites$n)
ggplot(sites, aes(x = exposition, y = n)) + geom_quasirandom()
ggplot(sites, aes(x = n)) + geom_histogram(binwidth = 0.03)
ggplot(sites, aes(x = n)) + geom_density()
```

@@

##### LOO Leave one out

>>>>

```{r echo = FALSE}
sites %>% group_by(exposition) %>% count(site)
boxplot(sites$n)
ggplot(sites, aes(x = exposition, y = n)) + geom_quasirandom()
ggplot(sites, aes(x = n)) + geom_histogram(binwidth = 0.03)
ggplot(sites, aes(x = n)) + geom_density()
```

@@

##### LOO (Leave one out)

### 2022-11-18 R/model_persistence_markdown.Rmd
Update

##### LOO-PIT: Leave one out probability integral transform checks

```{r}
p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
p2 <- ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
p1 / p2
plot(loo1)
plot(loo2)
```

>>>>

##### LOO (Leave one out)

```{r}
loo1
loo2
plot(loo1)
plot(loo2)
```

Leave one out probability integral transform

```{r}
p1 <- ppc_loo_pit_overlay(y, yrep1, lw = weights(loo1$psis_object))
p2 <- ppc_loo_pit_overlay(y, yrep2, lw = weights(loo2$psis_object))
p1 / p2
